\documentclass{article}
\begin{document}


\section{Technical Change Log}

\begin{description}

\item[2002-08-07 Greg McIntyre]\hspace{0em}

\begin{itemize}

\item Checked out first session's work and brutalised it, altering the directory structure by putting all .php and .html files into a subdirectory `web' and renaming, removing many files (such as functions.inc and include.inc), amalgamating the CVS `system' project by putting it in a subdirectory `docs'. Cleaned up a lot of code. 

\end{itemize}

\item[2002-08-14 Greg McIntyre]\hspace{0em}

\begin{itemize}

\item \textit{install.sh:} Wrote install script.
\item Updated directory structure to mirror CVS, making testing a CVS working directory easier. 

\end{itemize}

\item[2002-08-20 Greg McIntyre]\hspace{0em}

\begin{itemize}

\item \textit{plugin/README:} Wrote plugin specification.
\item \textit{install.sh:} Updated install script, removing references to `glob', which apparently is not a standard UNIX command. Replaced them with Bash's built-in globbing (e.g. echo *).

\end{itemize}

\item[2002-08-22 Greg McIntyre]\hspace{0em}

\begin{itemize}

\item \textit{plugins/shape:} Wrote new shape plugin, including generic C plugin framework (dgplugin.h, dgplugin.c).
\item \textit{docs/Makefile:} Removed nearly-duplicate Makefiles from subdirectories under docs, and made them include the common rules from docs/Makefile.
\item \textit{plugin/README:} Reworded a little to remove references to images (now `entities' as they may not be images). Clarified usage slightly. Updated examples.

\end{itemize}

\item[2002-08-29 Greg McIntyre]\hspace{0em}

\begin{itemize}

\item Imported work done this session to CVS.

\end{itemize}

\item[2002-08-30 Greg McIntyre]\hspace{0em}

\begin{itemize}

\item Moved the remainding global functions to classes.
\item Wrote initial framework for SQL database. SQL is to replace use of flat form database (ffdb). 
\item Implemented phpdocgen use (an internal documentation generator) and documented all classes used. 
\item \textit{web/admin.inc.php:} Created to handle database admin methods. Also documented.
\item \textit{web/session.inc.php, web/database\_admin.php:} Fixed problem where logging out of database admin caused currently logged in user from same browser to be logged off. Essentially, untied admin login and user login.
\item \textit{install.sh:} Fixed to work in conjunction with CVS.
\item \textit{web/plugin.inc.php:} Fixed plugin list to work in conjunction with CVS.
\item \textit{web/menu.php:} Made more attractive.
\item \textit{code/index.php:} Updated include files (was using old format).
\item \textit{web/index.html:} Displays welcome.php instead of home.php at startup.

\end{itemize}

\item[2002-09-02 Greg McIntyre]\hspace{0em}

\begin{itemize}

\item Implemented random gallery.
\item Implemented SQL database. (Still need attention to schema and primary keys). 

\end{itemize}

\item[2002-09-04 Greg McIntyre]\hspace{0em}

\begin{itemize}

\item Implemented copying entities between galleries, removing entities and evolving entities, along with all supported plugin options (randomness, method, number). 
\item \textit{web/system.inc.php:} Changed PHP\_SELF to SCRIPT\_NAME, as PHP\_SELF doesn't seem to work on CSE machines. SCRIPT\_NAME works.
\item \textit{web/welcome.php:} Added grey link to database admin page.
\item \textit{install.sh:} Fixed again. It wasn't recursing properly. Also updated to set execute permissions.
\item \textit{web/system.inc.php:} Empty array returned on error instead of false.
\item \textit{phpdocgen.pl:} Included this script to create internal documentation from the source.
\item Moved RandomGallery, Genepool and UserGallery classes out to their own files. 
\item Updated SQL database schema, simplifying and testing. Had to remove some primary keys, as they could not include variable length TEXT data (only the first 255 characters). 

\end{itemize}
\end{description}


\end{document}
